\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{soulutf8}


\setmainfont{Helvetica}
% \setmainfont{Proxima Nova}
% \setmainfont{Neue Haas Grotesk Display Pro}
% \setmainfont{Univers}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\thispagestyle{empty} % убрать нумерацию
\hyphenpenalty=10000 % убрать переносы

\titleformat
{\section}
[hang] 
{\bfseries\Large} % format
{\thesection} % label
{0.5em} % sep
{}[\vspace{-2ex}\rule{\textwidth}{0.5pt}] % before-sep after-sep
\titlespacing{\section}{0pc}{2ex}{0.5pc} % left - before - after spacings

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}

\begin{document}
\selectlanguage{english}
\begin{center}
    \Huge Dmitry Uspenskiy


    \small
    \begin{tabular}{ c|c|c }
        \textbf{uspenskiydmitry@gmail.com} & \textbf{t.me/black\_chick} & \textbf{github.com/wwwwwert} \\ 
    \end{tabular}
\end{center}

\section*{Education}
\textbf{NRU Higher School of Economics}\dotfill \textit{September 2020 - Present} \\
BS in Applied Mathematics and Computer Science. \\
Current program is Data Analysis and Intelligent Systems.
\begin{itemize}
    \item Third year. Full-time education. Government-funded position.
    \item \textit{Math courses studied}: Discrete Mathematics, Calculus, Linear Algebra and Geometry, 
    Algebra, Probability Theory and Mathematical Statistics, Fundamentals of Matrix Computations; \\ [0.8ex]
    \textit{Computer-Science courses studied}: Python, C++ Advanced, Algorithms and Data Structures, 
    Modern Software Engineering Practices, Computer Architecture and Operating Systems. 
\end{itemize}
\textbf{Correspondence Physical and Technical School}\dotfill \textit{September 2019 - May 2020}
\begin{itemize}
    \item Advanced Math and IT classes.
\end{itemize}
\textbf{Lycem №1535}\dotfill \textit{September 2018 - May 2020}
\begin{itemize}
    \item IT class with Yandex Lyceum programming course.
    \item Graduated with excellent and good grades.
\end{itemize}

\section*{Personal Projects}
\begin{itemize}
    \item \href{https://github.com/wwwwwert/structure_editor}
    {\textbf{Program for microstructure photographs analysis and particles dimensions evaluation}} \\
    \small {A program for creating markup in electron microscopy images and automatic visualization of its statistics. \\
    \textit{This work was \href{https://cs.hse.ru/cppr/best_projects}{rated} as one of the best in the educational program in 2022.}} \\
    {\footnotesize \textit{Frameworks used}: TKinter, OpenCV, NumPy, Seaborn \& MatPlotLib, Pandas, PyInstaller}

    \item \href{https://github.com/wwwwwert/sneaker_sales_bot}{\textbf{Sneaker sales bot}} \\
    \small {Bot that grabs sales from \textit{brandshop.ru} and notifies users interested in the items.} \\
    {\footnotesize \textit{Frameworks used}: BeautifulSoup, Telegram API with pyTelegramBotAPI library}

    \item \href{https://github.com/wwwwwert/footwear_page_bot}{\textbf{Footwear public page bot}} \\
    \small {Bot that parses articles from \textit{Hypebeast magazine} and posts their  translations with random music into \textit{VK} public page. \\
    Currently available at this \href{https://vk.com/footwear_damn}{public page}} \\
    {\footnotesize \textit{Frameworks used}: VK API, Google Translator API with deep-translator library, BeautifulSoup, Pandas}

\end{itemize}
\addcontentsline{toc}{section}{Unnumbered Section}

\section*{Technical Skills}
\begin{tabular}{ l p{12cm}l }
    \textbf{Programming Languages} & Python 3, C, C++, GNU Assembler, Bash, LaTex \\ [0.8ex]
    \textbf{Software \& Tools} & Shell, Git, SSH, GCC, GDB, CLion, PyCharm, VS Code, Jupyter \\ [0.8ex]
    \textbf{Technical Experience} & Neural Networks with PyTorch, Computer Vision, image processing, Python GUI, 
    data scrapping, data visualization, System calls, multithreading, messengers' API, 
    project deployment on Amazon AWS, Toloka-Kit API \\ [0.8ex]
    \textbf{Research Experience} & Matrix and sparse matrix calculations, creating mathematical models and recommender systems, 
    image processing and restoring, iterative methods, probability and statistics, analysis and complex analysis, data processing and labeling with crowdsourcing. \\ [0.8ex]
    \textbf{Languages} & ~~\llap{\textbullet}~~ English (fluent, passed Independent English Exam) \\
    & ~~\llap{\textbullet}~~ Russian (native)
\end{tabular}

\end{document}